%% CV_Javier_Rangel_2026.tex
%% Sources: CV_Javier_Rangel.pdf, DOC-20250130-WA0014 (older CV),
%%          cvAdvice.txt, mobile_audit_javier_implementation.md,
%%          auditoria_valor_javier_rangel.pdf, Photo-Portfolio/astroMigration branch

\documentclass[11pt, letterpaper]{article}

%% ─── PACKAGES ───────────────────────────────────────────────────────────────
\usepackage[
  top=0.55in, bottom=0.55in,
  left=0.65in, right=0.65in
]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{microtype}
\usepackage{multicol}
\usepackage{array}
\usepackage{booktabs}

%% ─── HYPERREF SETUP ─────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

%% ─── TYPOGRAPHY ─────────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

%% Section headings: small caps, ruled
\titleformat{\section}
  {\scshape\large}
  {}
  {0em}
  {}
  [\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

%% Subsection (company name)
\titleformat{\subsection}[runin]
  {\bfseries}
  {}
  {0em}
  {}
\titlespacing{\subsection}{0pt}{4pt}{4pt}

%% ─── CUSTOM COMMANDS ────────────────────────────────────────────────────────
% \entry{Left}{Right}  — two-column header row
\newcommand{\entry}[2]{%
  \noindent
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    #1 & #2
  \end{tabular*}%
}

% Job header: \job{Company}{Location}{Title}{Date}
\newcommand{\job}[4]{%
  \entry{\textbf{#1} \hspace{4pt} #2}{}%
  \\[1pt]%
  \entry{\textit{#3}}{\textit{#4}}%
}

% Project header: \project{Name}{Stack}
\newcommand{\project}[2]{%
  \noindent\textbf{#1} \hspace{4pt} \textit{| #2}%
}

\newenvironment{cvlist}{%
  \begin{itemize}[
    leftmargin=1.4em,
    itemsep=1.5pt,
    topsep=3pt,
    parsep=0pt
  ]
}{%
  \end{itemize}%
}

%% ─────────────────────────────────────────────────────────────────────────────
\begin{document}
\pagestyle{empty}

%% ═══════════════════════════════════════════════════════════
%%  HEADER
%% ═══════════════════════════════════════════════════════════
\begin{center}
  {\Huge\bfseries Javier Rangel Murillo}\\[4pt]
  Mexico City, Mexico\\[2pt]
  \href{mailto:inspecjrm@gmail.com}{inspecjrm@gmail.com}
  \enspace|\enspace
  \href{https://linkedin.com/in/javierramu2004}{linkedin.com/in/javierramu2004}
  \enspace|\enspace
  \href{https://github.com/JavierRangel2004}{github.com/JavierRangel2004}
  \enspace|\enspace
  \href{https://jrmgraphy.com}{jrmgraphy.com}
\end{center}

%% ═══════════════════════════════════════════════════════════
%%  PROFESSIONAL SUMMARY
%% ═══════════════════════════════════════════════════════════
\section{Professional Summary}

Founding Backend \& Mobile Engineer with end-to-end product ownership across
a full platform stack. Proven track record designing, building, and operating
enterprise-grade distributed backend systems and cross-platform mobile
applications in high-velocity startup environments.
Specialized in \textbf{Node.js} (TypeScript), \textbf{React Native} (Expo),
\textbf{Python}, and \textbf{Google Cloud Platform}, with deep focus on
system architecture, resilient integrations, and cost-optimization.
Currently pursuing a Bachelor's in Data Intelligence and Cybersecurity.

%% ═══════════════════════════════════════════════════════════
%%  EXPERIENCE
%% ═══════════════════════════════════════════════════════════
\section{Experience}

%% ── LegalTec ────────────────────────────────────────────────────────────────
\job{LegalTec}{Mexico City, Mexico}
    {Founding Backend \& Mobile Systems Engineer}{Oct 2025 -- Present}

\vspace{2pt}
\textit{Backend Platform}

\begin{cvlist}
  \item Led the end-to-end design, architecture, and development of a
        scalable backend system (178\,K+ live LOC, 91.6\% sole authorship)
        for a legal-tech startup using \textbf{Node.js}, \textbf{TypeScript},
        and \textbf{Express.js} with a domain-driven, DI-based architecture.

  \item Designed a robust cloud infrastructure leveraging
        \textbf{Google Cloud Platform} (Cloud Run, Cloud Tasks, Pub/Sub,
        KMS, Secret Manager, Storage) and \textbf{Firebase}
        (Auth, Firestore) for high availability and distributed processing.

  \item Engineered Puppeteer-based document verification pipelines for
        official Mexican identity documents (\textbf{CURP}/RENAPO and
        \textbf{SEP C\'edula Profesional}), eliminating dependency on
        costly external APIs.

  \item Built a distributed background-job system using \textbf{BullMQ}
        and \textbf{Redis} with 11 specialized workers (payment retry,
        hold cleanup, Google Meet event processing, recording TTL,
        verification pipeline, vault recurring charges, and more).

  \item Implemented full payment infrastructure integrating
        \textbf{PayPal APIs} (Orders, Vault, Subscriptions, Webhooks)
        for appointment billing and recurring platform charges.

  \item Integrated \textbf{Google Workspace / Google Meet APIs} to
        automate meeting creation, event-lifecycle handling, and
        post-meeting video ETL processing.

  \item Secured sensitive data via \textbf{Google Cloud KMS}
        encryption at rest; implemented JWT authentication, RBAC,
        circuit breakers (Opossum), and advanced rate limiting.

  \item Delivered production observability stack: Prometheus metrics,
        structured logging (Pino), audit trail, alerting service, and
        full OpenAPI documentation (66 routes, 25 spec files).

  \item Provisioned and maintained infrastructure-as-code with
        \textbf{Terraform} on GCP; configured GitHub Actions CI/CD
        pipelines to Cloud Run (staging + production).
\end{cvlist}

\vspace{4pt}
\textit{Mobile Platform}

\begin{cvlist}
  \item Designed and implemented the cross-platform mobile application
        using \textbf{React Native} (Expo) and \textbf{TypeScript},
        fully integrated with the backend platform
        (8\,826 TypeScript/TSX lines across 89 tracked files).

  \item Architected mobile authentication and session lifecycle management
        with encrypted token storage (\textbf{Expo Secure Store}),
        refresh-token handling, and a queued refresh strategy to prevent
        parallel \texttt{401} races under network instability.

  \item Implemented \textbf{Firebase Cloud Messaging} push notifications,
        including device registration, foreground handling, and
        notification-triggered navigation flows.

  \item Developed modular domain layers for appointments, notifications,
        profile management, and dashboards using
        \textbf{TanStack Query}, \textbf{Axios}, and \textbf{Zustand}
        for state and data orchestration.

  \item Built role-aware routing architecture using \textbf{Expo Router}
        with session-hydration guards, profile-completion flows, and
        conditional polling strategies (30\,s -- 3\,min per appointment
        state) for real-time UX.
\end{cvlist}

\bigskip

%% ── UP iOS Dev Lab ──────────────────────────────────────────────────────────
\job{Universidad Panamericana -- iOS Development Lab}{Mexico City, Mexico}
    {Backend Development Lead}{Sep 2025 -- Present}

\begin{cvlist}
  \item Promoted to Backend Lead to mentor incoming students on
        \textbf{Python}, software architecture, Clean Code, and modern
        API development.
  \item Orchestrate technical planning for multiple university projects,
        leading the migration to microservices and \textbf{Docker}
        containerization.
\end{cvlist}

\vspace{4pt}

\entry{\textit{Backend Developer}}{\textit{Oct 2022 -- Sep 2025}}

\begin{cvlist}
  \item Developed and deployed production APIs with \textbf{Django} and
        \textbf{Flask} to support native Swift iOS applications.
  \item Designed and managed relational and NoSQL databases
        (\textbf{PostgreSQL}, \textbf{MongoDB}), optimizing query
        performance and ensuring strict data security.
\end{cvlist}

%% ═══════════════════════════════════════════════════════════
%%  HIGHLIGHTED PROJECTS
%% ═══════════════════════════════════════════════════════════
\section{Highlighted Projects}

\project{PhotoCat}%
        {Python, SigLIP2, YOLOv8, BLIP, NLTK, Machine Learning}

\begin{cvlist}
  \item Built an AI-powered local pipeline to classify and organize large
        photo libraries using \textbf{SigLIP2} zero-shot genre
        classification fused with \textbf{YOLOv8} object-evidence scoring
        and \textbf{BLIP} captioning.
  \item Implemented confidence-gated decisions (auto / review /
        title-inferred), audit CSV reporting, optional XMP metadata
        writing, and automatic genre-based directory organization.
  \item \href{https://github.com/JavierRangel2004/PhotoCat}{github.com/JavierRangel2004/PhotoCat}
\end{cvlist}

\vspace{4pt}

\project{Photo Portfolio}%
        {Astro, TypeScript, React, Tailwind CSS, i18n}

\begin{cvlist}
  \item Rebuilt personal photography portfolio as a full
        \textbf{Astro} static site with route-based
        \textbf{English / Spanish internationalization}, dynamic
        category navigation, and lazy-loaded gallery components.
  \item Implemented modular component architecture (Header, Footer,
        CategoryDropdown, photo display) with WCAG-aligned accessibility
        and responsive design optimized for mobile and desktop.
  \item Deployed at \href{https://jrmgraphy.com}{jrmgraphy.com};
        source: \href{https://github.com/JavierRangel2004/Photo-Portfolio}{github.com/JavierRangel2004/Photo-Portfolio}
\end{cvlist}

\vspace{4pt}

\project{Redes que Cambian}%
        {Django, Angular, PostgreSQL, Docker}

\begin{cvlist}
  \item Developed a platform to connect individuals with NGOs across
        Mexico, centralizing social-project information on a containerized
        infrastructure.
  \item Implemented modules for project management, volunteer
        coordination, and detailed metrics oversight; deployed for a
        local NGO.
  \item \href{https://github.com/JavierRangel2004/redes-que-cambian}{github.com/JavierRangel2004/redes-que-cambian}
\end{cvlist}

\vspace{4pt}

\project{Sustainability Certifications Platform}%
        {Django, PostgreSQL}

\begin{cvlist}
  \item Built and sold an API to a sustainability consultancy to help
        companies meet ESG standards; integrated self-assessment tools,
        custom consulting workflows, and a sustainable-supplier directory.
  \item \href{https://github.com/JavierRangel2004/sustentabilidad}{github.com/JavierRangel2004/sustentabilidad}
\end{cvlist}

\vspace{4pt}

\project{Wayfinder}%
        {C++, Graph Algorithms, CSV}

\begin{cvlist}
  \item CLI application for efficient campus route planning using graph
        structures and CSV data; supports shortest/longest-path queries
        across weighted node networks.
  \item Deployed for a university institution to improve internal
        mobility signage and visitor navigation.
  \item \href{https://github.com/JavierRangel2004/Wayfinder}{github.com/JavierRangel2004/Wayfinder}
\end{cvlist}

%% ═══════════════════════════════════════════════════════════
%%  EDUCATION
%% ═══════════════════════════════════════════════════════════
\section{Education}

\entry{%
  \textbf{Universidad Panamericana (UP)} \hspace{4pt} Mexico City, Mexico
}{%
  \textit{Aug 2022 -- Jun 2027}
}\\
\textit{Bachelor of Engineering in Data Intelligence and Cybersecurity}

%% ═══════════════════════════════════════════════════════════
%%  TECHNICAL SKILLS
%% ═══════════════════════════════════════════════════════════
\section{Technical Skills}

\setlength{\tabcolsep}{0pt}
\begin{tabular}{@{}p{1.55in}p{\dimexpr\textwidth-1.55in}@{}}
  \textbf{Languages}
  & TypeScript, JavaScript, Python, C++, Rust, PHP \\[3pt]

  \textbf{Backend}
  & Node.js, Express.js, Django, Flask \\[3pt]

  \textbf{Mobile}
  & React Native (Expo), Expo Router, NativeWind \\[3pt]

  \textbf{Frontend / Web}
  & Astro, React, Angular, Tailwind CSS \\[3pt]

  \textbf{Cloud \& Infra}
  & Google Cloud Platform (Cloud Run, KMS, Pub/Sub, Tasks, Storage,
    Secret Manager), Firebase / Firestore, Docker, Terraform,
    GitHub Actions CI/CD \\[3pt]

  \textbf{Databases \& Queues}
  & PostgreSQL, MongoDB, Firestore, Redis, BullMQ \\[3pt]

  \textbf{State \& Networking}
  & TanStack React Query, Axios, Zustand,
    React Hook Form, Zod \\[3pt]

  \textbf{Observability}
  & Prometheus, Pino (structured logging), OpenAPI / Swagger,
    Circuit Breakers (Opossum) \\[3pt]

  \textbf{Tools \& Integrations}
  & PayPal API, Firebase Cloud Messaging, Twilio, SendGrid,
    Google Workspace APIs, Puppeteer, Jest, Git \\[3pt]

  \textbf{Languages}
  & Spanish (Native), English (C1 -- TOEFL iBT 607) \\
\end{tabular}

\end{document}
