%% CV_Javier_Rangel_2p.tex  —  Startup / Technical deep-dive version  (2 pages)
%% Follows cvAdvice.txt: action+tools+result bullets, curated skills,
%% all projects, architecture detail, both backend + mobile for LegalTec.

\documentclass[11pt, letterpaper]{article}

\usepackage[top=0.55in, bottom=0.55in, left=0.65in, right=0.65in]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[protrusion=true,expansion=false]{microtype}
\usepackage[T1]{fontenc}

\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\titleformat{\section}{\scshape\large}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\newcommand{\entry}[2]{%
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    #1 & #2
  \end{tabular*}}

\newenvironment{cvlist}{%
  \begin{itemize}[leftmargin=1.4em,itemsep=1.5pt,topsep=3pt,parsep=0pt]
}{\end{itemize}}

\newcommand{\project}[2]{\noindent\textbf{#1}\hspace{4pt}\textit{| #2}}

%% ─────────────────────────────────────────────────────────────────────────────
\begin{document}
\pagestyle{empty}

%% ── HEADER ──────────────────────────────────────────────────────────────────
\begin{center}
  {\Huge\bfseries Javier Rangel Murillo}\\[4pt]
  Mexico City, Mexico\\[2pt]
  \href{mailto:inspecjrm@gmail.com}{inspecjrm@gmail.com}
  \enspace|\enspace
  \href{https://linkedin.com/in/javierramu2004}{linkedin.com/in/javierramu2004}
  \enspace|\enspace
  \href{https://github.com/JavierRangel2004}{github.com/JavierRangel2004}
  \enspace|\enspace
  \href{https://jrmgraphy.com}{jrmgraphy.com}
\end{center}

%% ── SUMMARY ─────────────────────────────────────────────────────────────────
\section{Summary}

Backend and Mobile Engineer with startup experience building production systems
end-to-end across platform architecture, cloud infrastructure, and cross-platform
mobile delivery.
Sole author of 91.6\% of a production legal-tech backend (Node.js/TypeScript/GCP)
and full mobile client (React Native/Expo) — both integrated into a live platform.
Currently pursuing a Bachelor's in Data Intelligence and Cybersecurity.

%% ── SELECTED IMPACT ─────────────────────────────────────────────────────────
\section{Selected Impact}

\begin{cvlist}
  \item End-to-end backend architecture in startup environment — sole author of
        a production system handling payments, scheduling, identity verification,
        and video workflows.
  \item Cross-platform mobile implementation fully integrated with backend —
        auth lifecycle, push notifications, appointments, and profile management.
  \item Cloud infrastructure and CI/CD on Google Cloud — Terraform IaC, Cloud Run,
        GitHub Actions pipelines, Prometheus observability.
  \item Payments, notifications, and third-party integrations — PayPal, Google Meet,
        Firebase Cloud Messaging, Twilio, SendGrid, RENAPO, SEP.
  \item Technical mentorship and backend leadership — promoted to lead, guiding
        students and university engineering projects.
\end{cvlist}

%% ── EXPERIENCE ───────────────────────────────────────────────────────────────
\section{Experience}

\entry{\textbf{LegalTec} \quad Mexico City, Mexico}{}\\
\entry{\textit{Founding Backend \& Mobile Systems Engineer}}{\textit{Oct 2025 -- Mar 2026}}

\vspace{3pt}
\textit{Backend Platform}
\begin{cvlist}
  \item Architected and built the entire backend platform (Node.js, TypeScript, Express.js)
        with \textbf{91.6\% sole authorship} across 66 API routes, 78+ services, and 11
        background workers — taking a legal-tech startup from prototype to production.
  \item Designed a domain-driven, dependency-injected system on GCP (Cloud Run, Pub/Sub,
        Tasks, KMS, Secret Manager, Storage) with Firebase Auth/Firestore, enabling
        high-availability distributed processing and encryption at rest for sensitive data.
  \item Built 11 specialized workers with BullMQ + Redis (payment retry, hold cleanup,
        Google Meet event processing, video ETL, recording TTL, verification pipelines),
        supporting reliable async workflows across the platform.
  \item Enabled full platform monetization by integrating PayPal APIs (Orders, Vault,
        Subscriptions, Webhooks), supporting appointment billing and recurring charges
        with idempotent retry logic.
  \item Automated virtual appointment workflows via Google Workspace/Meet API (event
        lifecycle, meeting creation, post-meeting video ETL); integrated Twilio SMS
        verification and SendGrid transactional emails.
  \item Engineered Puppeteer-based scrapers for CURP/RENAPO and SEP C\'{e}dula
        Profesional validation, eliminating dependency on costly third-party APIs
        for Mexican identity verification.
  \item Delivered production observability: Prometheus metrics, Pino structured logging,
        audit trail, circuit breakers (Opossum), advanced rate limiting, and 25-file
        OpenAPI documentation suite.
  \item Provisioned and maintained infrastructure-as-code with Terraform on GCP;
        configured GitHub Actions CI/CD pipelines to Cloud Run for staging and
        production environments.
\end{cvlist}

\vspace{5pt}
\textit{Mobile Platform}
\begin{cvlist}
  \item Built cross-platform mobile app (React Native/Expo, 8\,826 TS/TSX lines across
        89 files) fully integrated with the backend — architected from routing bootstrap
        to domain feature delivery.
  \item Engineered secure session lifecycle management using Expo Secure Store with
        encrypted token storage, refresh-token handling, and a queued Axios interceptor
        strategy to prevent parallel 401 races under network instability.
  \item Enabled real-time push notifications via Firebase Cloud Messaging — device
        registration, foreground handling, and notification-driven navigation flows
        across the mobile app.
  \item Developed modular domain layers (appointments, notifications, profiles,
        dashboards) using TanStack Query, Zustand, and React Hook Form + Zod,
        with role-based data contracts and conditional polling per appointment state.
  \item Built role-aware routing with Expo Router: session-hydration guards, profile
        completion flows, and tab navigation — supporting lawyer and client personas.
\end{cvlist}

\bigskip

\entry{\textbf{Universidad Panamericana -- iOS Development Lab} \quad Mexico City, Mexico}{}\\
\entry{\textit{Backend Development Lead}}{\textit{Sep 2025 -- Present}}

\begin{cvlist}
  \item Promoted to lead to mentor incoming students on Python, clean architecture,
        and modern API development; guides technical planning for multiple university
        projects transitioning to microservices and Docker.
\end{cvlist}

\vspace{3pt}
\entry{\textit{Backend Developer}}{\textit{Oct 2022 -- Sep 2025}}

\begin{cvlist}
  \item Built and deployed production APIs with Django and Flask to support native
        Swift iOS applications; designed and managed PostgreSQL and MongoDB databases
        for performance and data security.
\end{cvlist}

%% ── HIGHLIGHTED PROJECTS ─────────────────────────────────────────────────────
\section{Highlighted Projects}

\project{Notadio}%
        {React/Vite, Express, TypeScript, whisper.cpp, Ollama, Python, FFmpeg}

\begin{cvlist}
  \item Built a local-first audio/video transcription application — processes media
        locally with whisper.cpp (no API costs) and generates structured AI summaries
        via Ollama using a MapReduce chunking pipeline for long transcripts.
  \item Implemented speaker diarization, SRT/JSON/TXT export, live progress telemetry
        (elapsed time, ETA, backend status), and an adaptive summarization fallback
        when LLM is unavailable.
  \item Deployed to a VPS as a single-user tool: Caddy reverse proxy, HTTP Basic Auth,
        and systemd service management; FFmpeg-based media normalization pipeline.
  \item \href{https://github.com/JavierRangel2004/Notadio}{github.com/JavierRangel2004/Notadio}
\end{cvlist}

\vspace{4pt}

\project{PhotoCat}%
        {Python, SigLIP2, YOLOv8, BLIP, NLTK, Machine Learning}

\begin{cvlist}
  \item AI-powered local pipeline to classify and organize large photo libraries
        using SigLIP2 zero-shot genre classification fused with YOLOv8
        object-evidence scoring and BLIP captioning.
  \item Confidence-gated decisions (auto / review / title-inferred), audit CSV
        reporting, optional XMP metadata writing, and automatic genre-based
        directory organization for streamlined curation workflows.
  \item \href{https://github.com/JavierRangel2004/PhotoCat}{github.com/JavierRangel2004/PhotoCat}
\end{cvlist}

\vspace{4pt}

\project{Redes que Cambian}%
        {Django, Angular, PostgreSQL, Docker}

\begin{cvlist}
  \item Platform to connect individuals with NGOs across Mexico; deployed for a
        local organization with modules for volunteer coordination, project
        management, and social-impact metrics.
  \item \href{https://github.com/JavierRangel2004/redes-que-cambian}{github.com/JavierRangel2004/redes-que-cambian}
\end{cvlist}

\vspace{4pt}

\project{Sustainability Certifications Platform}%
        {Django, PostgreSQL}

\begin{cvlist}
  \item Built and sold an API to a sustainability consultancy enabling companies
        to meet ESG standards — integrated self-assessment tools, custom consulting
        workflows, and a sustainable-supplier directory.
  \item \href{https://github.com/JavierRangel2004/sustentabilidad}{github.com/JavierRangel2004/sustentabilidad}
\end{cvlist}

\vspace{4pt}

\project{Photo Portfolio}%
        {Astro, TypeScript, React, Tailwind CSS, i18n}

\begin{cvlist}
  \item Rebuilt personal photography portfolio as a bilingual (EN/ES) Astro static
        site with route-based internationalization, dynamic category navigation, and
        lazy-loaded gallery components.
  \item Deployed at \href{https://jrmgraphy.com}{jrmgraphy.com} —
        \href{https://github.com/JavierRangel2004/Photo-Portfolio}{github.com/JavierRangel2004/Photo-Portfolio}
\end{cvlist}

\vspace{4pt}

\project{Wayfinder}%
        {C++, Graph Algorithms, CSV}

\begin{cvlist}
  \item CLI app for campus route planning using weighted graph structures and CSV
        data; supports shortest/longest-path queries — deployed for a university
        to improve visitor navigation.
  \item \href{https://github.com/JavierRangel2004/Wayfinder}{github.com/JavierRangel2004/Wayfinder}
\end{cvlist}

%% ── EDUCATION ─────────────────────────────────────────────────────────────────
\section{Education}

\entry{%
  \textbf{Universidad Panamericana (UP)} \quad Mexico City, Mexico
}{\textit{Aug 2022 -- Jun 2027}}\\
\textit{Bachelor of Engineering in Data Intelligence and Cybersecurity}

%% ── TECHNICAL SKILLS ──────────────────────────────────────────────────────────
\section{Technical Skills}

\setlength{\tabcolsep}{0pt}
\begin{tabular}{@{}p{1.6in}p{\dimexpr\textwidth-1.6in}@{}}
  \textbf{Core}
  & TypeScript, Node.js, Express.js, React Native (Expo), Python,
    GCP (Cloud Run, Pub/Sub, Tasks, KMS, Storage, Secret Manager),
    Firebase / Firestore, PostgreSQL, Redis \\[3pt]

  \textbf{Also used}
  & Django, Flask, Astro, React, Angular, Tailwind CSS, MongoDB,
    Terraform, Docker, GitHub Actions, BullMQ, TanStack Query,
    Zustand, React Hook Form, Zod, Expo Router, NativeWind,
    PayPal API, Firebase Cloud Messaging, Twilio, SendGrid,
    Google Workspace APIs, Puppeteer, Prometheus, Pino, OpenAPI,
    Opossum, Jest, C++, Rust, PHP \\[3pt]

  \textbf{Languages}
  & Spanish (native) \textbullet\ English C1 -- TOEFL iBT 607 \\
\end{tabular}

\end{document}
