%% CV_Javier_Rangel_EN_esteban.tex — English CV following Esteban's structure
%% March 2026

\documentclass[10pt, letterpaper]{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.6in, right=0.6in]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[protrusion=true,expansion=false]{microtype}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{amssymb}

\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

%% Section style: small caps + rule (matching Esteban's)
\titleformat{\section}{\scshape\large}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

%% Two-column header row
\newcommand{\entry}[2]{%
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    #1 & #2
  \end{tabular*}}

%% Compact bullet list
\newenvironment{cvlist}{%
  \begin{itemize}[leftmargin=1.4em,itemsep=1pt,topsep=2pt,parsep=0pt]
}{\end{itemize}}

%% Skill bar: 5 squares, #1 filled
\newcommand{\skillbar}[1]{%
  \foreach \i in {1,...,5}{%
    \ifnum\i>#1 $\square$\else $\blacksquare$\fi
  }%
}
\usepackage{pgffor}

%% ─────────────────────────────────────────────────────────────────────────────
\begin{document}
\pagestyle{empty}

%% ── HEADER ──────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Javier Rangel Murillo}\\[3pt]
  Mexico City, Mexico\\[1pt]
  \href{mailto:inspecjrm@gmail.com}{inspecjrm@gmail.com} \enspace|\enspace
  \href{https://linkedin.com/in/javierramu2004}{LinkedIn} \enspace|\enspace
  \href{https://github.com/JavierRangel2004}{GitHub}
\end{center}

%% ── PROFESSIONAL SUMMARY ───────────────────────────────────────────────────
\section{Professional Summary}

\textbf{Backend and Mobile Engineer} specialized in building production systems
end-to-end across platform architecture, cloud infrastructure, integrations,
and cross-platform mobile delivery. Experienced implementing \textbf{RESTful
APIs, background workers, payment systems, and identity verification pipelines}
using modern cloud-native architectures.

Proficient in designing and deploying backend platforms and mobile applications
using \textbf{TypeScript, Node.js, Express.js, React Native, GCP, and
event-driven systems}. Skilled in developing high-performance services for
real-time scheduling, monetization, and distributed async workflows.

Hands-on expertise with \textbf{cloud infrastructure on GCP (Cloud Run,
Pub/Sub, Tasks, KMS, Secret Manager), Firebase, Terraform IaC, and CI/CD
pipelines}. Experienced provisioning production environments with observability,
encryption at rest, and automated deployments.

Combines strong backend engineering with cross-platform mobile development
experience, enabling collaboration across infrastructure, product, and
engineering teams. Passionate about building reliable, scalable, and
maintainable production systems.

%% ── TECHNICAL SKILLS ────────────────────────────────────────────────────────
\section{Technical Skills}

\noindent
\begin{tabular*}{\textwidth}{@{}p{0.48\textwidth}@{\extracolsep{\fill}}p{0.48\textwidth}@{}}
  Programming (TypeScript, Python, SQL) \skillbar{5}
  & Backend (Node.js, Express, APIs) \skillbar{5} \\[4pt]
  Mobile (React Native, Expo) \skillbar{5}
  & Cloud \& Infra (GCP, Firebase, Terraform) \skillbar{4} \\[4pt]
  DevOps (Docker, CI/CD, GitHub Actions) \skillbar{4}
  & Databases (PostgreSQL, Redis, MongoDB) \skillbar{4} \\[4pt]
  Async Systems (BullMQ, Pub/Sub, Workers) \skillbar{4}
  & Integrations (PayPal, Twilio, SendGrid) \skillbar{4} \\[4pt]
  Frameworks (Django, Flask, Astro, React) \skillbar{4}
  & Developer Tools (Linux, Git, Puppeteer) \skillbar{5} \\
\end{tabular*}

%% ── PROFESSIONAL EXPERIENCE ────────────────────────────────────────────────
\section{Professional Experience}

\entry{\textbf{LegalTec}}{\textit{Founding Backend \& Mobile Engineer \enspace|\enspace Oct 2025 -- Mar 2026}}

\begin{cvlist}
  \item Architected and built the entire backend platform using \textbf{Node.js,
        TypeScript, and Express.js} as \textbf{91.6\% sole author} across 66 API
        routes, 78+ services, and 11 background workers --- taking a legal-tech
        startup from prototype to production.
  \item Designed \textbf{GCP infrastructure (Cloud Run, Pub/Sub, Tasks, KMS,
        Secret Manager, Firebase)} enabling high-availability distributed
        processing and encryption at rest for sensitive legal data.
  \item Built 11 specialized workers with \textbf{BullMQ + Redis} (payment retry,
        hold cleanup, Google Meet processing, video ETL, verification pipelines),
        enabling reliable async workflows at scale.
  \item Enabled full platform monetization via \textbf{PayPal APIs} (Orders,
        Vault, Subscriptions), automated \textbf{Google Meet} virtual appointments,
        and \textbf{Twilio/SendGrid} notification flows.
  \item Engineered \textbf{Puppeteer}-based scrapers for CURP/RENAPO and SEP
        C\'{e}dula validation, eliminating third-party API costs for Mexican
        identity verification.
  \item Built cross-platform mobile app (\textbf{React Native/Expo}, 8\,826
        TS/TSX lines, 89 files) with encrypted session lifecycle, token-refresh
        resilience, and role-aware navigation fully integrated with the backend.
  \item Enabled real-time push notifications via \textbf{Firebase Cloud Messaging},
        supporting device registration, foreground handling, and
        notification-driven routing across the app.
  \item Provisioned infrastructure-as-code with \textbf{Terraform} on GCP;
        configured \textbf{GitHub Actions} CI/CD pipelines to Cloud Run for
        staging and production environments.
\end{cvlist}

\medskip

\entry{\textbf{Universidad Panamericana -- iOS Development Lab}}{%
  \textit{Backend Development Lead \enspace|\enspace Oct 2022 -- Present}}

\begin{cvlist}
  \item Promoted to lead in Sep 2025; mentors students on \textbf{Python, clean
        architecture, and modern API design} while guiding multiple university
        projects to production.
  \item Built and deployed APIs with \textbf{Django and Flask} for native Swift
        iOS applications; managed \textbf{PostgreSQL and MongoDB} databases for
        performance and data security.
\end{cvlist}

%% ── PROJECTS & ACHIEVEMENTS ────────────────────────────────────────────────
\section{Projects \& Achievements}

\noindent\textbf{Notadio} (React/Vite, Express, TypeScript, whisper.cpp, Ollama, Python)

\begin{cvlist}
  \item Built a \textbf{local-first audio/video transcription} application ---
        processes media with \textbf{whisper.cpp} (no API costs) and generates
        AI summaries via \textbf{Ollama} using a MapReduce chunking pipeline
        for long transcripts.
  \item Implemented speaker diarization, SRT/JSON/TXT export, live progress
        telemetry; deployed to VPS with \textbf{Caddy} reverse proxy and
        systemd service management.
\end{cvlist}

\smallskip

\noindent\textbf{PhotoCat} (Python, SigLIP2, YOLOv8, BLIP, NLTK)

\begin{cvlist}
  \item AI pipeline that auto-classifies large photo libraries using
        \textbf{zero-shot genre classification} fused with object-evidence
        scoring and captioning; exports audit CSVs and writes XMP metadata
        for automated curation workflows.
\end{cvlist}

\smallskip

\noindent\textbf{Redes que Cambian} (Django, Angular, PostgreSQL, Docker)

\begin{cvlist}
  \item Platform connecting individuals with NGOs across Mexico; deployed for a
        local organization with modules for \textbf{volunteer management and
        social-project metrics}.
\end{cvlist}

\smallskip

\noindent\textbf{Photo Portfolio} (Astro, TypeScript, React, Tailwind CSS, i18n)

\begin{cvlist}
  \item Rebuilt personal photography portfolio as a \textbf{bilingual (EN/ES)
        Astro static site} with route-based internationalization, dynamic
        category navigation, and lazy-loaded gallery components. Live at
        \href{https://jrmgraphy.com}{jrmgraphy.com}.
\end{cvlist}

%% ── EDUCATION ───────────────────────────────────────────────────────────────
\section{Education}

\entry{\textbf{Universidad Panamericana} \quad Mexico City, Mexico}{}\\
\textit{Bachelor of Engineering in Data Intelligence and Cybersecurity}
\hfill \textit{Aug 2022 -- Jun 2027}

\medskip

\noindent\textbf{Languages:} Spanish (native) \textbullet\ English C1 -- TOEFL iBT 607

\end{document}
