%% CV_Javier_Rangel_1p.tex  —  Recruiter / ATS version  (1 page)
%% Follows cvAdvice.txt: concise bullets, action+tools+result, curated skills,
%% top 3 projects. No over-technical internals.

\documentclass[10pt, letterpaper]{article}

\usepackage[top=0.45in, bottom=0.45in, left=0.55in, right=0.55in]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[protrusion=true,expansion=false]{microtype}
\usepackage[T1]{fontenc}

\hypersetup{colorlinks=true, urlcolor=black, linkcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

%% Sections: small caps + rule
\titleformat{\section}{\scshape\normalsize}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{3pt}

%% Two-column header row
\newcommand{\entry}[2]{%
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    #1 & #2
  \end{tabular*}}

%% Compact bullet list
\newenvironment{cvlist}{%
  \begin{itemize}[leftmargin=1.2em,itemsep=0.5pt,topsep=2pt,parsep=0pt]
}{\end{itemize}}

%% ─────────────────────────────────────────────────────────────────────────────
\begin{document}
\pagestyle{empty}

%% ── HEADER ──────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Javier Rangel Murillo}\\[2pt]
  Mexico City, Mexico \enspace|\enspace
  \href{mailto:inspecjrm@gmail.com}{inspecjrm@gmail.com} \enspace|\enspace
  \href{https://linkedin.com/in/javierramu2004}{linkedin.com/in/javierramu2004} \enspace|\enspace
  \href{https://github.com/JavierRangel2004}{github.com/JavierRangel2004} \enspace|\enspace
  \href{https://jrmgraphy.com}{jrmgraphy.com}
\end{center}

%% ── SUMMARY ─────────────────────────────────────────────────────────────────
\section{Summary}

Backend and Mobile Engineer with startup experience building production systems
end-to-end across platform architecture, cloud infrastructure, integrations, and
cross-platform mobile delivery.
Strong focus on TypeScript, Node.js, React Native, and Google Cloud Platform.
Currently pursuing a Bachelor's in Data Intelligence and Cybersecurity.

%% ── EXPERIENCE ───────────────────────────────────────────────────────────────
\section{Experience}

\entry{\textbf{LegalTec} \quad Mexico City, Mexico}{}\\
\entry{\textit{Founding Backend \& Mobile Engineer}}{\textit{Oct 2025 -- Mar 2026}}

\smallskip
\textit{Backend}
\begin{cvlist}
  \item Architected and built the entire backend platform (Node.js, TypeScript, Express.js)
        as \textbf{91.6\% sole author} across 66 API routes — taking a legal-tech startup from
        prototype to production.
  \item Designed GCP infrastructure (Cloud Run, Pub/Sub, Tasks, KMS, Secret Manager, Firebase)
        enabling high-availability distributed processing and encryption at rest for sensitive
        legal data.
  \item Built 11 background workers with BullMQ + Redis (payment retry, scheduling, video ETL,
        verification pipelines), enabling reliable async workflows at scale.
  \item Enabled full platform monetization via PayPal APIs (Orders, Vault, Subscriptions),
        automated Google Meet virtual appointments, and Twilio/SendGrid notification flows.
  \item Engineered Puppeteer scrapers for CURP/RENAPO and SEP C\'{e}dula validation,
        eliminating third-party API costs for Mexican identity verification.
\end{cvlist}

\smallskip
\textit{Mobile}
\begin{cvlist}
  \item Built cross-platform mobile app (React Native/Expo, 8\,826 TS/TSX lines, 89 files)
        with encrypted session lifecycle, token-refresh resilience, and role-aware navigation.
  \item Enabled real-time push notifications via Firebase Cloud Messaging, supporting device
        registration, foreground handling, and notification-driven routing across the app.
  \item Developed domain modules (appointments, profiles, notifications) using TanStack Query
        and Zustand, accelerating cross-platform product delivery.
\end{cvlist}

\medskip

\entry{\textbf{Universidad Panamericana -- iOS Development Lab} \quad Mexico City, Mexico}{}\\
\entry{\textit{Backend Development Lead (promoted) \textnormal{|} Backend Developer}}%
      {\textit{Oct 2022 -- Present}}

\begin{cvlist}
  \item Promoted to lead in Sep 2025; mentors students on Python, clean architecture, and
        modern API design while guiding multiple university projects to production.
  \item Built and deployed APIs with Django and Flask for native Swift iOS applications;
        managed PostgreSQL and MongoDB databases for performance and data security.
\end{cvlist}

%% ── SELECTED PROJECTS ────────────────────────────────────────────────────────
\section{Selected Projects}

\noindent\textbf{Notadio} \textit{| React/Vite, Express, TypeScript, whisper.cpp, Ollama, Python}
\begin{cvlist}
  \item Full-stack local-first transcription app — processes audio/video with whisper.cpp
        and generates AI summaries via Ollama (MapReduce for long media); no API costs.
  \item Supports speaker diarization, SRT/JSON/TXT export, live progress telemetry;
        deployed to VPS with Caddy reverse proxy and systemd service management.
\end{cvlist}

\noindent\textbf{PhotoCat} \textit{| Python, SigLIP2, YOLOv8, BLIP, NLTK}
\begin{cvlist}
  \item AI pipeline that auto-classifies large photo libraries using zero-shot genre
        classification fused with object-evidence scoring and captioning; exports
        audit CSVs and writes XMP metadata for automated curation workflows.
\end{cvlist}

\noindent\textbf{Redes que Cambian} \textit{| Django, Angular, PostgreSQL, Docker}
\begin{cvlist}
  \item Platform connecting individuals with NGOs across Mexico; deployed for a local
        organization with modules for volunteer management and social-project metrics.
\end{cvlist}

%% ── EDUCATION ─────────────────────────────────────────────────────────────────
\section{Education}

\entry{\textbf{Universidad Panamericana (UP)} \quad
       \textit{B.Eng. in Data Intelligence and Cybersecurity}}%
      {\textit{Aug 2022 -- Jun 2027}}

%% ── TECHNICAL SKILLS ──────────────────────────────────────────────────────────
\section{Technical Skills}

\textbf{Core:} TypeScript \textbullet\ Node.js \textbullet\ Express.js \textbullet\
React Native (Expo) \textbullet\ Python \textbullet\ GCP \textbullet\
Firebase \textbullet\ PostgreSQL \textbullet\ Redis \textbullet\ Docker

\textbf{Also used:} Django \textbullet\ Flask \textbullet\ Astro \textbullet\
React \textbullet\ Angular \textbullet\ MongoDB \textbullet\ Terraform \textbullet\
BullMQ \textbullet\ TanStack Query \textbullet\ Zustand \textbullet\ PayPal API
\textbullet\ Twilio \textbullet\ SendGrid \textbullet\ Puppeteer \textbullet\
Jest \textbullet\ C++ \textbullet\ Rust

\textbf{Languages:} Spanish (native) \textbullet\ English C1 -- TOEFL iBT 607

\end{document}
